# Example Usage of agray Package

This document demonstrates how to use the agray grading functions for grading potato tubers.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
source("agray.r")
```

## Using default name and grading scheme
```{r default-grading}
grade(file = "example_data.csv")
```

This will output to a folder called 'example_data' within the current project directory.

## Supplying your own trial name
```{r custom-name}
grade(
  file = "example_data.csv",
  name = "Example trial"
)
```

This will output to a folder called 'Example trial' within the current project directory.

## Supplying the harvested area
```{r with-area}
grade(
  file = "example_data.csv",
  name = "Example trial with yield",
  area = 60
)
```

Now the output files will include additional columns for calculated yields.

## Custom tuber grades by size
```{r custom-size-grades}
# Remember the values are the minimum size for each class
size_grades <- list(
  "Large" = 3,
  "Med" = 2,
  "Small" = 1,
  "Undersize" = 0
)

grade(
  file = "example_data.csv",
  name = "Example trial - custom size grades",
  grades = size_grades,
  area = 60
)
```

## Custom tuber grades by weight
```{r custom-weight-grades}
weight_grades <- list(
  "8+ oz" = 8,
  "4-8 oz" = 4,
  "2-4 oz" = 2,
  "<2 oz" = 0
)

grade(
  file = "example_data.csv",
  name = "Example trial - custom weight grades",
  grades = weight_grades,
  grade_by = "Weight",
  area = 60
)
```
